Progressive Second Price Auction Mechanism for Data-Exchange Models

### 2019-10-02 body_acm.tex
Ty!

Users on the shared data plan given by \cite{att} do not ``buy" or ``sell"
data, however, we may easily augment the model to include a price function,
which may be virtual, creating a secondary market.
In order to demonstrate potential of expanding to other $\emph{a priori}$ use
models, we give a simple example. Consider Alice and Bob, who met through an online service connecting neighborly
individuals closest to each other, in fact, close enough to be within wireless
range. Alice is going on vacation, and offers to transfer her wireless signal to
Bob. As they have the same provider, Bob agrees, and is able to use Alice's
bandwidth, which he finds is useful during peak network
hours. He pays a discounted rate. We note that the additional bandwith may be
used by another device, or even a 5G-capable mobile device.

The secondary market provides a unique opportunity for social equilibrium, as it
allows users to share data without sharing the same data plan, a restriction in
most ISPs, such as \cite{att}. We reason that a secondary market effectively creates a competitive secondary market, and contributes to the
dynamics of a free-market economy. Market competition is a desirable quality in
free markets, and is encouraged, particularly in wireless and data services. In
fact, California Legistature has recently passed laws promoting
competition and enforcing fair practice of ISPs \cite{cabill}.
Laws such as \cite{fedbill} exist to
regulate ISPs as they have historically come close to monopolizing regional
markets, leading to consumer abuse.
The global view of privacy has not been addressed, as the data exchange model is still
in its experimental phase.
Within the secondary market, bid privacy is a concern for two reasons: (1) Buyers are reluctant to
reveal their true valuations, as sellers may use these values to discriminate
against specific buyers. (2) Buyers doubt an auction's outcome, as they do
not pay what they bid, e.g. the auctioneer might create a fake
second highest bid slightly below the highest bid in order to increase his revenue
In general, the buyer does not trust the auctioneer, and the economy does not
trust the ISP.
We therefore determine that our mechanism must be (3) globally and locally privacy-preserving.

The market
topology and the user strategy are organically determined by the impact of user
behavior on market dynamics, and so determines a minimally optimal objective
representing user valuation globally, and so fufills an additional property of
economy over time and space. To the best of our knowledge, this is the first
work to provide a comprehensive derivation of a truthful mechanism that is self-contained within a dynamic market
topology.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism that is self-contained within a dynamic market
topology.

In classic mechanism design, with multiple user types, there is no single
way to design the transformation from the direct revelation mechanism to its
corresponding computational design. We apply a modifier to the PSP mechanism in
order to mutate the strategy space, following dynamic user
correspendence. As in \cite{lazar}, we take the direct
approach by guessing the right modifier, and context, such that we have the
desired result by composition with the PSP rules. 
As in \cite{lazar}, the incentive for a
user to truthfully reveal its type is built into the user strategies. Then,
local equilibria follow as a result of incentive
compatibility characterizing best strategy moves.
We claim that our formulation holds the desired PSP qualities,
%converging at a rate of $\mathcal{O}(\sum_{i\in\mcI}(\sum_{j\in\mcI}) \theta_i /
%\epsilon I!)$.
%We note that the convergence time is 
and that our strategy profiles are natural; they depend on the ratio of
supply and demand, or the ratio of buyers to sellers.

We focus on providing users with an incentive framework, and
so rational users choose a collaborative exchage. 
The user strategies are organic in that they are natural, or
induced by the dynamic market itself. In other words, adhering to the second-price rule,
where price is derived from autonomous demand, we have a strategic
progressive auction, and a multi-objective equilibria.
This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space, Then, in the limit of
the data-model, a user reveals its valuation of a quantitiy of data-resource over the whole range of possible demands.

@@

Progressive second price auctions are used for optimal allocation in a
variety of scenarios, and for different reasons. Different definitions of social
welfare define different strategies. Typical goals of optimization are the
maximization of revenue, and optimal allocation. Other papers' focus, taken from
auction theory, optimize sellers' reserve price, or market price. Results derived from game theory
focus on player strategy, as in this work. In \cite{qpsp}, user strategy gives a ``quantized"
version of PSP, improving the rate of convergence of the game. Modifications to
the mechanism that result in improved convergence also appear in \cite{burst},
which relies on a global approximation function of demand.
Another mechanism derived from game theory \cite{diffserve}, derives
optimal strategies for buyers and brokers, and further shows the existence
of networkwide market equilibria by provisioning a dynamical system. The stability
of the game may be implied by various equilibria in distributed systems.

Allowing a user preference to, loosely, represent a policy, we may interpret
a user preference from the data exchange market as a meta-policy. Then,  plans allow users to set their own policies, and rely existing
framework for to implement their preferences. Several studies address the
security of policy-based network management.
Trusted management systems based on the
Common Informtion Model (CIM) focus on policy-based management, namely,
the ``Policy-Maker" toolkit. 
In general, the translation of policy-based management systems to SDN focuses on combining
the simplicity of policy-based implementation with the flexibility of SDN, as in the
meta-policy system, CIM-SDN \cite{meta}.

In the general context of distributed and decentralized allocation of
resources, a variety of equilibria exist for heterogeous and homogenous services
with the similar condition of truthfulness. In all cases, the PSP constraints are
sufficient to attain the desirable property of truthfulness through incentive
compatibility, as the pricing mechanism upholds the exclusion-compensation
principle.

@@

We construct the model for a PSP data auction for mobile users
particpating in secondary mobile data exchange market.
Let the set of all wireless users to be labeled by
the index set $\mcI = \lbrace 1, \cdots, I\rbrace$. In our current formulation, we do not allow a seller to host multiple
auctions, thus we may assume that data is a unary resource belonging to the seller, and
identify each local auction with the index of the seller
$j\in\mcI$. The bid profiles of the users are given as,
$s \equiv
[s_i^j] \in \mcI \times \mcI$,  
We have the strategy space for buyer $i$ as all possible bids at all auctions:
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \big( \Pi_{k\ne
i\in\mcI} S_k^j\big)$ as the
associated opponent profiles.

The grid of bid profiles, $s$, represents the state of distributed PSP auction
mechanism in the secondary market. 
We emphasize that we allow the grid $s$ to represent the bids of all buyers and
sellers. In general, we will not reference the full grid. In order to emphasize
that a bid belongs to a seller, we use the notation $\s_i^j$. We
will also empasize the \emph{context} of the bid to indicate the user type.
To further clarify our analysis, we adopt the notational conventions: a
seller's profile is denoted by $\s^j = [s_i^j]_{i\in\mcI}$, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyer's profile, where $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents.
Furthermore, noting that this is a simplification for ease of notation, we let
$D^j = \sum_{i\in\mcI} d_i^j$ be the total amount of data $j$ has to sell, and
$D_i = \sum_{j\in\mcI} d_i^j$ represent the total amount of data desired by buyer $i$.

We assume a public platform, published by the ISP, that allows sellers to advertise their
auctions, and that buyers may submit bids directly to sellers over the wireless
network. 
The ISP is included
by introducing a mutation of user type, and represent
the ISP as a blind, deaf user $\kappa$, who does not participate
in any auctions, but nonetheless holds the power to create a monopoly
.
We assume that buyers and sellers are
separated (a seller does not also buy data and vice versa). 
In general, we denote a buyer's identity $i \in \mcI$, and a seller as
$j\in\mcI$.
Suppose $i$ is buying from $j$. We assume that a user's budget is 
sufficient, as the alternative would be to pay a higher price to the ISP. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. 
Seller $j$'s local auction begins at time $t>0$. The seller takes reponsibility
to send opponent bid profiles $s_{-i}$ to each buyer that joins the auction,
those buyers where $s_i^j > 0 \in s$, as well its own bid, $\s_i^j = (d_i^j,
p_i^j)$, offfering quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$, 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$. 
Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j=\s_i^j = 0$. A buyer that does not submit a bid will not recieve opponent profiles from seller
$j$. We additionally determine that a user who does not submit a bid is holding
to the previous bid, either zero or nonzero. We note that buyers are
consistently referenced using the index $i$ as a subscript, and sellers using
the index $j$ as a superscript, as in \cite{semret}.

@@

We aim to design a distributed PSP auction, operating within a strategic framework that
determines the bidding behavior of users in a wireless network.
The auction design must must meet a certain set of known
criteria: (1) \emph{truthfulness}, (2) \emph{individual rationality/
selfishness}, (3) \emph{social welfare maximization}, and (4)\emph{the winning
bid is persistent private information}. For the secondary data exchange
market, we determine that the
strategy space must meet additional criteria: (5) \emph{privacy and
independence from the ISP}, (6) \emph{locally fair division}, and (7)
\emph{minimize crossover in buyer/ seller pools}.
Thus, we propose a mechanism that promotes social welfare. 
Thus our motivation to adapt the PSP auction. The PSP auction given in
\cite{lazar} is comprised of a set of simple and symmetric rules that closely
follow market theory, and as it is distributed we can require privacy.

We first address the clear need for privacy in the secondary data exchange market. In \cite{zheng},
it is assumed that the ISP interferes in 2cm (market) dynamics, and will maximize the
gap between supply and demand in each transaction, exacting the difference as
revenue. We notice that this market behavior is suspiciously monopolistic, as a
single entity, the ISP, holds a global market power. It is further claimed in
\cite{zheng} that user bids are truthful as they are guaranteed to receive
their bid. We argue that this model represents an ``unwitting" buyer and an
equally uninformed seller, as they have no intution of fair market value.
Thus, in the interest of social good, we aim to provide a method to arrest
anti-competitive conduct by ISPs. Then, we may trust the ISP. Naturally,
rational users will only purchase data if the rewards outweigh the risk, it follows that
the secondary auction should be trusted as well. 
We argue that as the mechanism is also privacy-preserving, that both the users and the ISP benefit.
An ISP that is trusted will end up with a loyal customer base, taking profit
from to one that is revenue maximizing, assuming that competion laws will
prevent a monopoly.

We define a value to be private if any coalition is incapable of learning any information
besides what can be inferred from the shared computation and the coalition’s
inputs. We describe the process as given in \cite{felix}. In general, a distributed private
computation, where buyer $i$ is part of a coalition comprising auction $j$, is as follows:

Denoting $m_{-i} = [(s_i^j, r_i), m_1, \cdots, m_n]_{k\ne i\in \mcI}$, buyer sends a
message to each of its opponents, where $s_i^j$ is $i$'s bid, $r_i$
is an independent random value, and $m_1, \cdots, m_n$ the messages $i$ has
received so far.
Then, all buyers are able to confirm the winning bid $s_{\bar{i}}^*$.

The
private computation process requires that buyers connect with each other, and
so reveal their identities to the coalition. It was proven in \cite{felix} that full privacy is not possible in a second
price auction, even if we allow partial relevation and weak coalitions. Yet, we
claim that our mechanism is trustworthy:

\subsubsection{Buyers are anonymous}
In our secondary market, we have that any local auction is anonymous by definition, as a permutation of
the valuations resutls in a permutation of allocations and prices, equivalently,
exchanging the bids of two losing buyers does not change the auction's result.
Formally,
\definition{(Anonymous auction)} \cite{felix}
Given an auction $j$ and buyers $i\in\mcI$, a protocol for computing
$\max\lbrace i \in\mcI : p_i^j \ge p_k^j \ \forall \ k\in\mcI\rbrace$ if for
all coalitions $T\subset \mcI$, any pair of inputs $x = [s_1^j, \cdots,
s_I^j], \xi$, so that $\xi$ is a permutation of $x$, $\forall \ i \in T : x_i =
\xi_i$, and $\max( )$, and any choice of random inputs $\lbrace
r_i\rbrace_{i\in T}$. Let $\bar{T} =   T \times \mcI \setminus T$, 
$$
    Pr\big([x, \lbrace r_i\rbrace_{i\in T}]_{x\in}
    \big\vert
    \lbrace r_i\rbrace_{i\in T}\big) = Pr\big([\xi, \lbrace r_i\rbrace_{i\in T}]_{\xi\in T
    \times \mcI \setminus T}\big\vert
    \lbrace r_i\rbrace_{i\in T}\big)),
$$
which states that any two inputs, the messages seen by coalition $T$
are indentically distributed.

\subsubsection{The winning bid is persistent private information.}
We claim that a buyer's trust in a local auction is fufilled when the outcome of
the auction is guaranteed to be correct, and if the winner's identity is secret.
For each local auction, we define a coalition of the
participating buyers. The winning bidder is \emph{privately} chosen by
distributing the computation of the winner to the local coalition. The
computation is based on the homomorphicity of secret sharing. We present the
Lemma in its general form,
{
\lemma{(Benaloh 1987)}\label{modp} \ 
    $f(x_1, x_2, \cdots, x_n) = \sum_{i=1}^n x_i \mod p$ is privately
    computable.
}
Thus, it is possible to privately compute,
\begin{equation}\label{winner}
    \omega = \max([p_i^j]_{i\in\mcI^j}) = (p_1^j, p_2^j, \cdots, p_n^j, \argmax(p^j).
\end{equation}
We have the following procedure determining the winner of auction $j$ for
some fixed time in the bid progression, where $D^j > 0$.
% PRIVACY
\begin{center}
\begin{algorithm}
\caption{(Max bid private computation)}
\begin{algorithmic}[1]\label{maxbidcomp}
\State $\omega\gets 1, e\gets 0$
\While{$e \le 1$}
\For{$i \in \mcI^j$}
\If{$p_i^j \le \omega$}
\State $p_i^j \gets 1 $
\Else
\State $p_i^j \gets 0$
\EndIf
\EndFor
\State $e = \sum_{i\in\mcI^j} p_i^j \mod (n+1)\quad$ (Lemma \ref{modp})
\For{$i \in \mcI^j$}
\If{$p_i^j \ge e$}
\Return $i \ (winner)$
\EndIf
\EndFor
\EndWhile\\
\end{algorithmic}
\end{algorithm}
\end{center}

The winning buyer then leaves the auction, and so we have that the privacy of
the winning bid is persistent. We note that it is possible for a winner to
anonymously rejoin an auction, however this does not alter our result.

\subsubsection{Privacy and independence from the ISP.}
In our model, privacy is integrated into the mechanism. Our design enforces
privacy by hiding the reserve price of the sellers. At time
$t=0$, a seller $j$ entering the market will
submit bid $\s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
platform, and so the initial bid $\s_\kappa^j$, is public knowledge. 
The auction
begins at time $t>0$, and at $t=0$, $j$ will
initializing its reserve price by executing a single bid iteration.
Sellers do not update pricing information with the ISP, thereby hiding
its local market price in the data-exchange market. As the ISP has limited
information from its ``competitor", it is unable to sabatoge prices derived
from fair market competition.
Thus, we claim that our model supports and protects the secondary market, allowing it
to be in direct competition with its parent ISP, and so contributes to the
regulation of ISPs \cite{fedbill} and supports a regional free-market economy
with respect to wireless data \cite{cabill}.
We will assume that the cost of participating in the secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. We do not model ISP revenue, but assume it may be extracted from the
bid fee at $t=0$.

We now proceed to formally define the PSP auction, which determines the actions 
buyers and sellers in the secondary market, and which we will denote the \emph{data}
PSP rules. 
We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
will determine its bid quanities by,
\begin{equation}\label{opt-out}
    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
\end{equation}
In a general sense, $\g_i$ applies our user strategy to the PSP rules.

@@

and is interpreted as the aggragate of minimum prices that buyer $i$ bids in

@@

the total minimum price for the buyer cannot be an aggragation of the

@@

the total price cannot be an aggragation of the

@@

\subsubsection{Truthfulness.}
We will prove that the dominant strategy for buyers is to submit coordinated bids,
where all bids the buyer submits are equal. Our motivation for coordinated bids
comes from the idea of potential games. In potential games, the
incentive of all users to change strategy can be expressed as a single global
function. We map the incentive of a buyer over all auctions $j\in\mcI$ to a
single potential function. This is a standard method that is used often, as it
simplfies the analysis of both strategy and auction design. We will prove the necessary condition of an $\epsilon$-best
reply: a new bid price must differ from the last by at least $\epsilon$.
Thus, our strategic bid is an $\epsilon$-best response.

@@

We define a move to a better market position to be synonymous with a
strategic bid. \\ 
\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
from auction design and game theory, respectively.\\
Our mechanism allows a buyer
to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
utility while minimizing the number of positive bids submitted to the overall
market. 
% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ \g_i(a) - c_i,
\end{equation}
where the composition of the elastic valuation function $\theta_i$ with $\g_i$
distributes a buyers' valuation of allocation $a$ across local markets (and thus
multiple sellers).
In this way we extend the PSP rules described
in \cite{semret} to design equilibria across subsets of local data-exchange markets.

@@

The topology of the bids in $\delta$ is key to our result. We immediately have:

@@

that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision

@@

%Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.

>>>>

Users on the shared data plan given by \cite{att} do not ``buy" or ``sell"
data, however, we may easily augment the model to include a price function,
which may be virtual, creating a secondary market.
In order to demonstrate potential of expanding to other $\emph{a priori}$ use
models, we give a simple example. Consider Alice and Bob, who met through an online service connecting neighborly
individuals closest to each other, in fact, close enough to be within wireless
range. Alice is going on vacation, and offers to transfer her wireless signal to
Bob. As they have the same provider, Bob agrees, and is able to use Alice's
bandwidth, which he finds is useful during peak network
hours. He pays a discounted rate.

The secondary market provides a unique opportunity for social equilibrium, as it
allows users to share data without sharing the same data plan, a restriction in
most ISPs, such as \cite{att}. We reason that a secondary market effectively creates a competitive secondary market, and contributes to the
dynamics of a free-market economy. Market competition is a desirable quality in
free markets, and is encouraged, particularly in wireless and data services. In
fact, California Legislature has recently passed laws promoting
competition and enforcing fair practice of ISPs \cite{cabill}.
Laws such as \cite{fedbill} exist to
regulate ISPs as they have historically come close to monopolizing regional
markets, leading to consumer abuse.
The global view of privacy has not been addressed, as the data exchange model is still
in its experimental phase.
Within the secondary market, bid privacy is a concern for two reasons: (1) Buyers are reluctant to
reveal their true valuations, as sellers may use these values to discriminate
against specific buyers. (2) Buyers doubt an auction's outcome, as they do
not pay what they bid, e.g. the auctioneer might create a fake
second highest bid slightly below the highest bid in order to increase his revenue
In general, the buyer does not trust the auctioneer, and the economy does not
trust the ISP.
We therefore determine that our mechanism must be (3) globally and locally privacy-preserving.

The market
topology and the user strategy are organically determined by the impact of user
behavior on market dynamics, and so determines a minimally optimal objective
representing user valuation globally, and so fulfills an additional property of
economy over time and space. To the best of our knowledge, this is the first
work to provide a comprehensive derivation of a truthful mechanism that is self-contained within a dynamic market
topology.
To the best of our knowledge, this is the first work to provide a comprehensive
derivation of a truthful mechanism that is self-contained within a dynamic market
topology.

In classic mechanism design, with multiple user types, there is no single
way to design the transformation from the direct revelation mechanism to its
corresponding computational design. We apply a modifier to the PSP mechanism in
order to mutate the strategy space, following dynamic user
correspondence. As in \cite{lazar}, we take the direct
approach by guessing the right modifier, and context, such that we have the
desired result by composition with the PSP rules. 
As in \cite{lazar}, the incentive for a
user to truthfully reveal its type is built into the user strategies. Then,
local equilibria follow as a result of incentive
compatibility characterizing best strategy moves.
We claim that our formulation holds the desired PSP qualities,
%converging at a rate of $\mathcal{O}(\sum_{i\in\mcI}(\sum_{j\in\mcI}) \theta_i /
%\epsilon I!)$.
%We note that the convergence time is 
and that our strategy profiles are natural; they depend on the ratio of
supply and demand, or the ratio of buyers to sellers.

We focus on providing users with an incentive framework, and
so rational users choose a collaborative exchange. 
The user strategies are organic in that they are natural, or
induced by the dynamic market itself. In other words, adhering to the second-price rule,
where price is derived from autonomous demand, we have a strategic
progressive auction, and a multi-objective equilibria.
This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space, Then, in the limit of
the data-model, a user reveals its valuation of a quantity of data-resource over the whole range of possible demands.

@@

Progressive second price auctions are used for optimal allocation in a
variety of scenarios, and for different reasons. Different definitions of social
welfare define different strategies. Typical goals of optimization are the
maximization of revenue, and optimal allocation. Other papers' focus, taken from
auction theory, optimize sellers' reserve price, or market price. Results derived from game theory
focus on player strategy, as in this work. In \cite{qpsp}, user strategy gives a ``quantized"
version of PSP, improving the rate of convergence of the game. Modifications to
the mechanism that result in improved convergence also appear in \cite{burst},
which relies on a global approximation function of demand.
Another mechanism derived from game theory \cite{diffserve}, derives
optimal strategies for buyers and brokers, and further shows the existence
of network-wide market equilibria by provisioning a dynamical system. The stability
of the game may be implied by various equilibria in distributed systems.

Allowing a user preference to, loosely, represent a policy, we may interpret
a user preference from the data exchange market as a meta-policy. Then,  plans allow users to set their own policies, and rely existing
framework for to implement their preferences. Several studies address the
security of policy-based network management.
Trusted management systems based on the
Common Information Model (CIM) focus on policy-based management, namely,
the ``Policy-Maker" toolkit. 
In general, the translation of policy-based management systems to SDN focuses on combining
the simplicity of policy-based implementation with the flexibility of SDN, as in the
meta-policy system, CIM-SDN \cite{meta}.

In the general context of distributed and decentralized allocation of
resources, a variety of equilibria exist for heterogeneous and homogeneous services
with the similar condition of truthfulness. In all cases, the PSP constraints are
sufficient to attain the desirable property of truthfulness through incentive
compatibility, as the pricing mechanism upholds the exclusion-compensation
principle.

@@

We construct the model for a PSP data auction for mobile users
participating in secondary mobile data exchange market.
Let the set of all wireless users to be labeled by
the index set $\mcI = \lbrace 1, \cdots, I\rbrace$. In our current formulation, we do not allow a seller to host multiple
auctions, thus we may assume that data is a unary resource belonging to the seller, and
identify each local auction with the index of the seller
$j\in\mcI$. The bid profiles of the users are given as,
$s \equiv
[s_i^j] \in \mcI \times \mcI$,  
We have the strategy space for buyer $i$ as all possible bids at all auctions:
$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \big( \Pi_{k\ne
i\in\mcI} S_k^j\big)$ as the
associated opponent profiles.

The grid of bid profiles, $s$, represents the state of distributed PSP auction
mechanism in the secondary market. 
We emphasize that we allow the grid $s$ to represent the bids of all buyers and
sellers. In general, we will not reference the full grid. In order to emphasize
that a bid belongs to a seller, we use the notation $\s_i^j$. We
will also emphasize the \emph{context} of the bid to indicate the user type.
To further clarify our analysis, we adopt the notational conventions: a
seller's profile is denoted by $\s^j = [s_i^j]_{i\in\mcI}$, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyer's profile, where $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents.
Furthermore, noting that this is a simplification for ease of notation, we let
$D^j = \sum_{i\in\mcI} d_i^j$ be the total amount of data $j$ has to sell, and
$D_i = \sum_{j\in\mcI} d_i^j$ represent the total amount of data desired by buyer $i$.

We assume a public platform, published by the ISP, that allows sellers to advertise their
auctions, and that buyers may submit bids directly to sellers over the wireless
network. 
The ISP is included
by introducing a mutation of user type, and represent
the ISP as a blind, deaf user $\kappa$, who does not participate
in any auctions, but nonetheless holds the power to create a monopoly
.
We assume that buyers and sellers are
separated (a seller does not also buy data and vice versa). 
In general, we denote a buyer's identity $i \in \mcI$, and a seller as
$j\in\mcI$.
Suppose $i$ is buying from $j$. We assume that a user's budget is 
sufficient, as the alternative would be to pay a higher price to the ISP. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. 
Seller $j$'s local auction begins at time $t>0$. The seller takes responsibility
to send opponent bid profiles $s_{-i}$ to each buyer that joins the auction,
those buyers where $s_i^j > 0 \in s$, as well its own bid, $\s_i^j = (d_i^j,
p_i^j)$, offering quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$, 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$. 
Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j=\s_i^j = 0$. A buyer that does not submit a bid will not receive opponent profiles from seller
$j$. We additionally determine that a user who does not submit a bid is holding
to the previous bid, either zero or nonzero. We note that buyers are
consistently referenced using the index $i$ as a subscript, and sellers using
the index $j$ as a superscript, as in \cite{semret}.

@@

We aim to design a distributed PSP auction, operating within a strategic framework that
determines the bidding behavior of users in a wireless network.
The auction design must must meet a certain set of known
criteria: (1) \emph{truthfulness}, (2) \emph{individual rationality/
selfishness}, (3) \emph{social welfare maximization}, and (4)\emph{the winning
bid is anonymous}. For the secondary data exchange
market, we determine that the
strategy space must meet additional criteria: (5) \emph{privacy and
independence from the ISP}, (6) \emph{locally fair division}, and (7)
\emph{minimize crossover in buyer/ seller pools}.
Thus our motivation to adapt the PSP auction. The PSP auction given in
\cite{lazar} is comprised of a set of simple and symmetric rules that closely
follow market theory, and as it is distributed we can require privacy. We describe the process as given in \cite{felix}. In general, a distributed
computation, where buyer $i$ is part of a coalition comprising auction $j$, is as follows:

Denoting $m_{-i} = [(s_i^j, r_i), m_1, \cdots, m_n]_{k\ne i\in \mcI}$, buyer sends a
message to each of its opponents, where $s_i^j$ is $i$'s bid, $r_i$
is an independent random value, and $m_1, \cdots, m_n$ the messages $i$ has
received so far. Then, all buyers are able to confirm the winning bid $s_{\bar{i}}^*$. 
It was proven in \cite{felix} that full privacy is not possible in a second price auction, even if we allow partial revelation and weak coalitions. We propose anonymity, in the winning bid only.

\subsubsection{Buyers are anonymous}
In our secondary market, we have that any local auction is anonymous by definition, as a permutation of
the valuations results in a permutation of allocations and prices, equivalently,
exchanging the bids of two losing buyers does not change the auction's result.
Formally,
\definition{(Anonymous auction)} \cite{felix}
Given an auction $j$ and buyers $i\in\mcI$, a protocol for computing
$\max\lbrace i \in\mcI : p_i^j \ge p_k^j \ \forall \ k\in\mcI\rbrace$ if for
all coalitions $T\subset \mcI$, any pair of inputs $x = [s_1^j, \cdots,
s_I^j], \xi$, so that $\xi$ is a permutation of $x$, $\forall \ i \in T : x_i =
\xi_i$, and $\max( )$, and any choice of random inputs $\lbrace
r_i\rbrace_{i\in T}$. Let $\bar{T} =   T \times \mcI \setminus T$, 
$$
    Pr\big([x, \lbrace r_i\rbrace_{i\in T}]_{x\in}
    \big\vert
    \lbrace r_i\rbrace_{i\in T}\big) = Pr\big([\xi, \lbrace r_i\rbrace_{i\in T}]_{\xi\in T
    \times \mcI \setminus T}\big\vert
    \lbrace r_i\rbrace_{i\in T}\big)),
$$
which states that any two inputs, the messages seen by coalition $T$
are identically distributed.

\subsubsection{The winning bid is trusted (anonymous) information.}
We claim that a buyer's trust in a local auction is fulfilled when the outcome of
the auction is guaranteed to be correct, and if the winner's identity remains private information. For each local auction, we define a coalition to be the
participating buyers. The winning bidder is chosen by
distributed computation via homomorphic encryption. We present the Lemma in its general form,
{
\lemma{(Benaloh 1987)}\label{modp} \ 
    $f(x_1, x_2, \cdots, x_n) = \sum_{i=1}^n x_i \mod p$ is privately
    computable.
}
Thus, it is possible to anonymously compute,
\begin{equation}\label{winner}
    \omega = \max([p_i^j]_{i\in\mcI^j}) = (p_1^j, p_2^j, \cdots, p_n^j, \argmax(p^j).
\end{equation}
We have the following procedure determining the winner of auction $j$ for
some fixed time in the bid progression, where $D^j > 0$.
% PRIVACY
\begin{center}
\begin{algorithm}
\caption{(Max bid private computation)}
\begin{algorithmic}[1]\label{maxbidcomp}
\State $\omega\gets 1, e\gets 0$
\While{$e \le 1$}
\For{$i \in \mcI^j$}
\If{$p_i^j \le \omega$}
\State $p_i^j \gets 1 $
\Else
\State $p_i^j \gets 0$
\EndIf
\EndFor
\State $e = \sum_{i\in\mcI^j} p_i^j \mod (n+1)\quad$ (Lemma \ref{modp})
\For{$i \in \mcI^j$}
\If{$p_i^j \ge e$}
\Return $i \ (winner)$
\EndIf
\EndFor
\EndWhile\\
\end{algorithmic}
\end{algorithm}
\end{center}

The winning buyer then leaves the auction, and so we have that the privacy of
the winning buyer is persistent. We note that it is possible for a winner to
anonymously rejoin an auction, however this does not alter our result. At time
$t=0$, a seller $j$ entering the market will
submit bid $\s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
platform, and so the initial bid $\s_\kappa^j$, is public knowledge. 
The auction begins at time $t>0$, and at $t=0$, $j$ will
initializing its reserve price by executing a single bid iteration.

%We will assume that the cost of participating in the secondary market is
%absorbed by the bid fee, which could represent data used in submitting bids, or
%a fee charged per unit of data, or a flat rate charged at the completion of the
%purchase. We do not model ISP revenue, but assume it may be extracted from the bid fee at $t=0$.

We now proceed to formally define the PSP auction, which determines the actions 
buyers and sellers in the secondary market, and which we will denote the \emph{data}
PSP rules. 
We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
part of its type. Buyer $i$, when determining how to acquire a possible allocation $a$,
will determine its bid quantities by,
\begin{equation}\label{opt-out}
    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
\end{equation}
In a general sense, $\g_i$ applies our user strategy to the PSP rules.

@@

and is interpreted as the aggregate of minimum prices that buyer $i$ bids in

@@

the total minimum price for the buyer cannot be an aggregation of the

@@

the total price cannot be an aggregation of the

@@

\subsubsection{Truthfulness.}
We will prove that the dominant strategy for buyers is to submit coordinated bids,
where all bids the buyer submits are equal. Our motivation for coordinated bids
comes from the idea of potential games. In potential games, the
incentive of all users to change strategy can be expressed as a single global
function. We map the incentive of a buyer over all auctions $j\in\mcI$ to a
single potential function. This is a standard method that is used often, as it
simplifies the analysis of both strategy and auction design. We will prove the necessary condition of an $\epsilon$-best
reply: a new bid price must differ from the last by at least $\epsilon$.
Thus, our strategic bid is an $\epsilon$-best response.

@@

In any market, a buyer or seller would like to obtain the maximum amount of utility 
possible while staying within budget. The buyer's utility maximizes the amount of 
data allocated by the seller, while the seller's utility maximizes the cost of the 
data sold.
We may illustrate the resulting product space for the buyer,
\vspace{-0.3in}
{
\begin{center}\begin{figure}[H]\caption{Product / Quotient Space}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
  {
     a & p \\
     d &  \\};
  \path[-stealth]
    (m-1-1) edge node [left] {projection} (m-2-1)
            edge node [above] {level} (m-1-2)
    (m-1-2) edge [dashed,-] (m-2-1);
\end{tikzpicture}
\end{figure}\end{center}
}
\vspace{-0.3in}
The `level', or price associated with the buyer's bid may be projected onto a line. As we 
will show, holds when buyers use the same bid price for all nonzero bids. The `projection',
or the amount of data requested, is a plane, since buyers may bid in more than
one auction. Clearly, the allocation is the product of the price and the data request.
There is, however, another logical representation, that the buyer has found an allocation that
satisfies its demand AND price constraints.
We define a move to a better market position to be synonymous with a
strategic bid. \\ 
\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangeable,
from auction design and game theory, respectively.\\
Our mechanism allows a buyer
to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
utility while minimizing the number of positive bids submitted to the overall
market.
% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ \g_i(a) - c_i,
\end{equation}
where the composition of the elastic valuation function $\theta_i$ with $\g_i$
distributes a buyers' valuation of allocation $a$ across local markets (and thus
multiple sellers). Thus, the composition map (the codomain of $\theta_i(\g_i)$ is the
same as the domain of $\g_i(a)$) performs the function of restricting
the buyer's domain to minimize $d^j p^j - c_i$, i.e., maximize $u_i$.
Using this intuition, we formally extend the PSP rules described
in \cite{semret} to design equilibria across subsets of local data-exchange markets.

@@

@@

that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposition

@@

%Finally, we note that $z_i^j$ does not increase the aggregate demand of the buyer.
